Localisation and Sensor Privacy Using the Extended Information Filter and Secure Weighted Aggregation

### 2020-07-23 main.tex
Couple more of the points from the ITI meeting added to dot points to make sure they're not forgotten Started trying to make the network/sensor subsets picture in tikz but it's a nightmare. Files remain for the time being

Passive attacks only from sensors to learn navigator position (Otherwise could do some kind of attack that would send fake measurement and note the change in it's own measurements - possible this would give away average of other sensors' measurements but unclear). Justify by saying sensors need to behave for localisation to work in the first place, for example GPS.

@@

Fixed sensor subsets of which only whole subsets can be used at once. Maybe a picture of what this might look like in a high level distributed localisation diagram.

@@

\subsection{Localisation Measurement Modification}
Show here the weighted integrals that give mean and variance of the new noise. If wanting to show more working, do this in appendix section, but probablynot needed.

@@

@@

% Maybe name the scheme? That would be in the heading here
\subsection{Algorithm}
Piece together the whole algorithm here.

>>>>

Passive attacks only from sensors to learn navigator position (Otherwise could do some kind of attack that would send fake measurement and note the change in it's own measurements - possible this would give away average of other sensors' measurements but unclear). Any largly incorrect inputs from sensors may also be detectable by comparison to alternative navigator onboard sensors (GPS etc.). Justify by saying sensors need to behave for localisation to work in the first place.

@@

Fixed sensor subsets of which only whole subsets can be used at once. Maybe a picture of what this might look like in a high level distributed localisation diagram. Should consider that this subt grouping would also mean the leakage of the average sensor/measurment of each subset not all sensors at once. This should be considered when choosing sensor subsets and locations.

@@

\subsection{Localisation Measurement Modification}
Show here the weighted integrals that give mean and variance of the new noise. If wanting to show more working, do this in appendix section, but probably not needed.

@@

Additionally increased range accuracy may be possible when sensors know the process model of the navigator, allowing them to run their own filter (more accurate than only measumrements but not as accurate as the navigator's estimate from multiple sensors) and use their filtered estimated distance as the scaling factor when computing the modified measurement variance.

@@

% Maybe name the scheme? That would be in the heading here
\subsection{Algorithm}
Piece together the whole algorithm here.
Give the algorithm as a pseudocode (including encoding and encryption)
